Something about Euro, EMU, and Inflation

### 2010-07-23 pkg/paper/Draft/draft-Z-W.tex
cleaned bib changes in gloglisfit: estimate moments with exp(par) due to log estimation in ML
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/glogis@30 b679b2f7-6539-45d0-a605-5ddcb976cde9

The main problem is to determine the number of classes k (data is grouped into k classes where we then calculate the difference between observed and expected frequencies). In a continuous distribution case, there are no natural boundaries. 
As given in \citet{kendal} the maximum likelihood estimation of the parameters is not a big problem if k is large enough. The classes are taken to cover equal ranges of the variate, which can be done easily once k is determined. This procedure was advocated by Mann and Gumberl. One rule would be to let k be equal to  $3.765(N-1)^{2/5}$ for a 5\% significance level, when using intervals with equal probability under $H_0$, as given in \citet{boreo}. We use this rule with a range of [3,2*k-3] for the tests and report any pvalues below 0.05.

@@

>>>>

The main problem is to determine the number of classes k (data is grouped into k classes where we then calculate the difference between observed and expected frequencies). In a continuous distribution case, there are no natural boundaries. 
As given in \citet{kendal} the maximum likelihood estimation of the parameters is not a big problem if k is large enough. The classes are taken to cover equal ranges of the variate, which can be done easily once k is determined. This procedure was advocated by Mann and Gumberl. One rule would be to let k be equal to  $3.765(N-1)^{2/5}$ for a 5\% significance level, when using intervals with equal probability under $H_0$, as given in \citet{boero}. We use this rule with a range of [3,2*k-3] for the tests and report any pvalues below 0.05.

@@

\newpage
